Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-23 parts/stelmass.tex

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
estimates to within 0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.

@@

>>>>

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with M/L estimates from population synthesis
models.  In principle, a detailed analysis of the spectral energy
distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
estimates to within 0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}.  There is some
evidence from spectral lines that massive galaxies tend to have a more
bottom-heavy IMF than the Milky Way, but a much higher stellar
mass-to-light would over-predict the mass in some lensing systems
\citep{2015MNRAS.454L..71S}.

@@

Figure~\ref{fig:stelmass} shows most of the candidates having stellar
and total mass typical of massive ellipticals.  SW05 is one of the
most massive of all the candidates, with a mass of galaxy-group scale.
It is a particularly attractive system for follow-up observations at
higher resolution, as it is a large system with clear multiple-image
features, and modelling leaves little doubt that it is a lens.  SW04
seems to be even more massive, but the diagnostics leave some doubts
about this model.  The two lowest-mass systems, SW19 and SW42, are
important if they are indeed lenses, as they would be low-mass lenses
dominated by dark matter.  All the modelled systems have reasonable
stellar-mass fractions, except for two cases where the stellar-mass
fraction is too low (halo-matching index $>1$): these are SW42 and
SW57.  In the case of SW57, the model has poor diagnostics and should
be discounted.  The model for SW42, on the other hand, is quite
convincing --- except for the high halo-matching index.  If SW42 turns
out not to be a lens, that would support the halo-matching index as an
effective criterion for filtering models.
